\large UNet-HCRF Integration for Sequence Labeling on EEG Data

### 2024-12-09 manuscript/slides.tex
add results

@@

>>>>

\begin{frame}{Mean Field Inference in HCRF}
\centering
\resizebox{.95\textwidth}{!}{
\begin{algorithm}[H]
\caption{Mean-field inference in fully-connected CRF}
\KwIn{$Q_i(h_i) \gets U_i(h_i), \; i = 1, 2, \dots, N$
\tcp*[f]{Initialize $Q(h)$}}
\While{not reach max iteration number}{
$\hat{Q}_i^{(m)}(h_i) \gets \sum_{j \neq i} k^{(m)}(f_i, f_j) Q_j(h_i)$ for all
$m$ \tcp*[f]{Message Passing}\;
$\tilde{Q}_i^{(m)}(h_i) \gets \sum_{l \in \mathcal{L}} \mu^{(m)}(h_i, l)
\sum_m \omega^{(m)} \hat{Q}_i^{(m)}(l)$ \tcp*[f]{Compatibility Transform}\;
$Q_i(h_i) \gets \exp \{\phi(h_j, x_j; \omega) + \varphi(y, h_j, x_j; \delta)
- \tilde{Q}_i(x_i)\}$ \tcp*[f]{Local Update}\;
Normalize $Q_i(h_i)$\;
}
\end{algorithm}}
\end{frame}

@@

\begin{frame}
\frametitle{Training Schedule}
The loss function was designed as Kullback-Leibler (KL) divergence.
\begin{figure}[tbp]
\centering
\includegraphics[width=.55\textwidth]{pretrain}
\vspace{-.3em}
\caption{Pre-train UNet learning rate schedule.}
\end{figure}
\vspace{-1.2em}
\begin{figure}[tbp]
\centering
\includegraphics[width=.55\textwidth]{finetune}
\vspace{-.3em}
\caption{Fine tuning HCRF learning rate schedule.}
\end{figure}
\end{frame}

\section{Results and Conclusion}

\begin{frame}{Results}
We evaluate our model by 5 fold cross-validation.
\bigskip
\begin{itemize}
\item Our model achieves a \textbf{0.4992} KL-divergence.
\bigskip
\item The baseline model from Kaggle using EfficientNet obtains a 0.59
cross-validation KL-divergence.
\end{itemize}
\bigskip
However, there still are many teams on Kaggle have achieved even lower
KL-divergence scores (0.2-0.3) by leveraging the power of large models
like Vision Transformers (ViT).
\end{frame}

\begin{frame}{Conclusion}
\begin{itemize}
\item We build a Hidden Conditional Random Fields for EEG based Spectrograms
image classification.
\bigskip
\item The latent CRF layer is desgined to capture the latent segmentation
information of the output of Neural Networks.
\bigskip
\item A variational mean-field inference scheme is used to address the
posterior distribution.
\bigskip
\item We integrate the Unet and HiddenCRF into an end-to-end training structure.
The Neural Networks feature learning and variational inference can be
accelerated jointly by GPUs.
\end{itemize}
\end{frame}
